Are mental properties supervenient on brain properties?

### 2011-08-05 nature_sci_rep/submission2/supervenience.tex
finished redline cep comments of aug 5 2011
defined beta_min

In other words, we can \emph{never} reject $L^*>0$ in favor of supervenience, no matter how much data we obtain.  
Supervenience therefore does not satisfy Popper's falsifiability criterion \cite{Popper1959}.

@@

Unfortunately, the rate of convergence of $L_{F}(g_n)$ to $L_{F}(g^*)$ depends on the (unknown) distribution $F=F_{MB}$ \cite{DGL96}. Furthermore, arbitrarily slow convergence theorems regarding the rate of convergence of $L_{F}(g_n)$ to $L_{F}(g^*)$ demonstrate that there is no universal $n,n'$ which will guarantee that the test has power greater than any specified target $\beta > \alpha$ \cite{Devroye83}. For this reason, the test outlined above can provide only a one-sided conclusion: if we reject we can be $100(1-\alpha)$\% confident that $\MeB$ holds, but we can never be confident in its negation; rather, it may be the case that the evidence in favor of $\MeB$ is insufficient 
% for any number of reasons, including that 
because we simply have not yet collected enough data. 
% Thus, without restrictions on $F_{MB}$, arbitrarily slow convergence theorems imply that our theorem of $\varepsilon$-supervenience does not \tr{strictly} satisfy Popper's {\it falsifiability} requirement \cite{Popper}.
This leads immediately to the following theorem:
\begin{thm} \label{thm:4}
There is no universal $n,n'$ that guarantees $\beta \geq \beta_{min}>\alpha$.
\end{thm}

>>>>

In other words, we can \emph{never} reject $L^*>0$ in favor of supervenience, no matter how much data we obtain.

@@

Unfortunately, the rate of convergence of $L_{F}(g_n)$ to $L_{F}(g^*)$ depends on the (unknown) distribution $F=F_{MB}$ \cite{DGL96}. Furthermore, arbitrarily slow convergence theorems regarding the rate of convergence of $L_{F}(g_n)$ to $L_{F}(g^*)$ demonstrate that there is no universal $n,n'$ which will guarantee that the test has power greater than any specified target $\beta > \alpha$ \cite{Devroye83}. For this reason, the test outlined above can provide only a one-sided conclusion: if we reject we can be $100(1-\alpha)$\% confident that $\MeB$ holds, but we can never be confident in its negation; rather, it may be the case that the evidence in favor of $\MeB$ is insufficient 
% for any number of reasons, including that 
because we simply have not yet collected enough data. 
% Thus, without restrictions on $F_{MB}$, arbitrarily slow convergence theorems imply that our theorem of $\varepsilon$-supervenience does not \tr{strictly} satisfy Popper's {\it falsifiability} requirement \cite{Popper}.
This leads immediately to the following theorem:
\begin{thm} \label{thm:4}
For any target power $\beta_{min} > \alpha$, there is no universal $n,n'$ that guarantees $\beta \geq \beta_{min}$.
\end{thm}

% Moreover, switching the null and alternative hypotheses---yielding $H_0^{\eps'}: L^*<\eps$ and $H_A^{\eps'}: L^* \geq \eps$---does not resolve the matter.
Therefore, even $\eps$-supervenience does not satisfy Popper's falsifiability criterion \cite{Popper1959}.
